\documentclass[10pt,letterpaper]{article}

\usepackage[margin=0.36in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{array}
\usepackage{tabularx}
\usepackage{xcolor}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\setlength{\tabcolsep}{0pt}
\renewcommand{\arraystretch}{1.0}
\linespread{0.93}

\definecolor{accent}{HTML}{0F766E}
\definecolor{textgray}{HTML}{374151}

\newcommand{\name}[1]{%
  {\Large\bfseries #1}\par\vspace{1pt}
}

\newcommand{\contact}[1]{%
  {\footnotesize #1}\par\vspace{4pt}
}

\newcommand{\sectiontitle}[1]{%
  \vspace{3pt}
  {\normalsize\bfseries\color{accent} #1}\par
  \vspace{1pt}
  {\color{accent}\hrule height 0.6pt}
  \vspace{2pt}
}

\newcommand{\entry}[4]{%
  \begin{tabularx}{\textwidth}{@{}X r@{}}
    {\bfseries #1} & {\footnotesize\bfseries #2} \\
    {\footnotesize\textit{#3}} & {\footnotesize #4}
  \end{tabularx}
  \vspace{1pt}
}

\newcommand{\projectentry}[2]{%
  {\bfseries #1}\hfill{\footnotesize #2}\par
  \vspace{1pt}
}

\newenvironment{tightitems}{%
  \begin{itemize}
    \setlength{\itemsep}{0pt}
    \setlength{\parskip}{0pt}
    \setlength{\parsep}{0pt}
    \setlength{\topsep}{1pt}
    \setlength{\leftmargin}{12pt}
}{%
  \end{itemize}
  \vspace{0pt}
}

\begin{document}
\fontsize{9.25}{10.2}\selectfont
\raggedright

\name{Saarthak Saxena}
\contact{\href{mailto:saarthaksaxena7@gmail.com}{saarthaksaxena7@gmail.com} \textbar{}
\href{https://www.linkedin.com/in/saarthakiiitd/}{linkedin.com/in/saarthakiiitd} \textbar{}
\href{https://github.com/Saarthakkj}{github.com/Saarthakkj} \textbar{}
\href{https://x.com/curlysaarthak}{x.com/curlysaarthak}}

\sectiontitle{Experience}

\entry{Applied AI Intern}{\textbf{Mar 2026 -- May 2026}}{Brace.so}{}
\begin{tightitems}
  \item \textbf{Data Pipeline \& Optimization:} Designed and shipped a relationship-scoring strategy that reduced posts processed by \textbf{97\%} (\textbf{2,186 to 64} data points) while retaining \textbf{98\%} of high-quality relationship signals, validated through \textbf{60+} controlled experiments across \textbf{72} profiles and \textbf{\textasciitilde{}90K} baseline relationship records. Built the quality score using recency, engagement, virality controls, top-result filtering, and reaction limits, then reduced third-party API usage by consolidating a multi-step workflow into a single pass and cutting external API calls per profile refresh by \textbf{\textasciitilde{}60\%}.
  \item \textbf{Search \& Ranking:} Rebuilt people search ranking so expanded LLM queries could enforce exact role, company, and location requirements, replacing soft score cutoffs with deterministic filtering for structured searches.
  \item \textbf{Knowledge Graph \& Taxonomy:} Built an autonomous skill-taxonomy maintenance engine that extracts skills and tools from profile text, ranks evidence with semantic similarity and usage patterns, and classifies terms into parent-child categories.
  \item \textbf{Decision Quality:} Built a review system that revisits uncertain skill matches after collecting more evidence across batches.
  \item \textbf{Connection Path Finding:} Built a path expansion system that finds direct and indirect relationship paths up to \textbf{3} degrees away across \textbf{\textasciitilde{}4,700} profiles and \textbf{\textasciitilde{}11,600} relationship links, evaluating \textbf{3.4M+} candidate path checks and \textbf{29.3M} possible route combinations to improve candidate selection. Achieved a \textbf{99.87\%} path-finding success rate with \textbf{87.69\%} best-candidate selection accuracy using threshold-based selection, validated across \textbf{9} strategies and multiple profile-connectivity segments.
\end{tightitems}

\entry{UG Researcher}{\textbf{Jan 2025 -- Present}}{A\textbf{2}A Lab, IIIT Delhi}{On Site}
\begin{tightitems}
  \item Optimized embedded systems performance through targeted code and hardware improvements.
  \item Developed an intuitive UI for visualizing complex system performance metrics.
\end{tightitems}

\entry{ML Engineer}{\textbf{Jun 2025 -- Nov 2025}}{Stealth Startup}{Contract work: \textbf{Jul 2025 -- Oct 2025}}
\begin{tightitems}
  \item \textbf{Business Impact:} Built the core ML infrastructure that helped the client secure a \textbf{INR 30 Lac (\textasciitilde{}\$35k)} research grant.
  \item \textbf{Custom Tooling:} Adapted and extended GraphGym source code to ingest custom molecular embeddings, enabling automated experimentation across \textbf{48k} data points.
  \item \textbf{Massive Scale:} Orchestrated \textbf{1,000,000+} optimization trials on remote distributed GPUs and beat Chemprop, the industry standard.
  \item \textbf{Rapid Delivery:} Shipped a production-ready, lightweight \textbf{2M}-parameter inference API in \textbf{8} weeks, handling the full lifecycle from data ingestion to AWS deployment using FastAPI and Docker.
\end{tightitems}

\entry{Software Engineering Intern}{\textbf{Jan 2024 -- May 2024}}{HeydoTech}{}
\begin{tightitems}
  \item Used Python libraries including OpenCV and PyAutoGUI to develop \textbf{2} automation tools for internal projects.
  \item Collaborated with cross-functional teams of \textbf{5+} members to implement feature enhancements, improving system performance for approximately \textbf{100} users.
  \item Contributed to UI/UX improvements that enhanced overall user experience, measured by positive feedback from \textbf{80\%} of test users.
\end{tightitems}

\sectiontitle{Projects}

\projectentry{Underwater Mysid Detection}{CV, Deep Learning, PyTorch, YOLOv\textbf{8} \textbar{} \textbf{Jan 2025 -- Present}}
\begin{tightitems}
  \item Built a CV pipeline for near-transparent mysid detection in underwater scenes, reaching \textbf{0.61} mAP\textbf{50} with augmented \textbf{38--114} image datasets and YOLOv\textbf{8}-seg improvements over U-Net baselines.
\end{tightitems}

\projectentry{Detoxify: Distraction Filter}{Python, JS, MLOps, Gemini API \textbar{} \textbf{Jan 2025 -- Present}}
\begin{tightitems}
  \item Built a Chrome extension using Gemini AI to classify YouTube batches in \textbf{1.95s}, analyzing \textbf{8--12} videos per batch and surfacing alerts for distracting content.
\end{tightitems}

\projectentry{\href{https://github.com/Saarthakkj/docbook}{Docbook}}{Python, GraphRAG, CLI \textbar{} \textbf{Apr 2025 -- Present}}
\begin{tightitems}
  \item GraphRAG-based CLI tool for intelligent documentation context extraction.
  \item Converts a single URL input into a full knowledge graph using crawl\textbf{4}ai, with automated semantic search and retrieval.
\end{tightitems}

\projectentry{Ghibli Image Scraper}{JS, Chrome Ext API, Gemini AI \textbar{} \textbf{Mar 2025}}
\begin{tightitems}
  \item Created a Chrome extension using Gemini AI to detect and download Ghibli-style art from X.com, earning GitHub Projects Community visibility.
\end{tightitems}

\projectentry{\href{https://github.com/Saarthakkj/course_reccomendation}{Bayesian Course Recommendation System}}{Python, PyTorch, Bayesian ML \textbar{} \textbf{2025}}
\begin{tightitems}
  \item Achieved \textbf{0.915} AUC using Bayesian Personalized Ranking for implicit feedback.
  \item Implemented matrix factorization with BPR optimization and probabilistic handling for cold-start recommendations.
\end{tightitems}

\sectiontitle{Education}

\entry{BTech, Electronics and Communication Engineering}{\textbf{Nov 2022 -- Present}}{IIIT Delhi}{}

\end{document}
