\documentclass[10pt,letterpaper]{article}

\usepackage[margin=0.42in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{array}
\usepackage{tabularx}
\usepackage{xcolor}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\setlength{\tabcolsep}{0pt}
\renewcommand{\arraystretch}{1.0}
\linespread{0.95}

\definecolor{accent}{HTML}{0F766E}
\definecolor{textgray}{HTML}{374151}

\newcommand{\name}[1]{%
  {\Large\bfseries #1}\par\vspace{1pt}
}

\newcommand{\contact}[1]{%
  {\footnotesize #1}\par\vspace{2pt}
}

\newcommand{\sectiontitle}[1]{%
  \vspace{1pt}
  {\normalsize\bfseries\color{accent} #1}\par
  \vspace{0.5pt}
  {\color{accent}\hrule height 0.6pt}
  \vspace{1pt}
}

\newcommand{\entry}[4]{%
  \begin{tabularx}{\textwidth}{@{}X r@{}}
    {\bfseries #1} & {\footnotesize\bfseries #2} \\
    {\footnotesize\textit{#3}} & {\footnotesize #4}
  \end{tabularx}
  \vspace{0pt}
}

\newcommand{\projectentry}[2]{%
  {\bfseries #1}\hfill{\footnotesize #2}\par
  \vspace{0.5pt}
}

\newenvironment{tightitems}{%
  \begin{itemize}
    \setlength{\itemsep}{0pt}
    \setlength{\parskip}{0pt}
    \setlength{\parsep}{0pt}
    \setlength{\topsep}{0pt}
    \setlength{\leftmargin}{10pt}
    \setlength{\itemindent}{0pt}
}{%
  \end{itemize}
  \vspace{-2.5pt}
}

\begin{document}
\fontsize{9.5}{10.6}\selectfont
\raggedright

\name{Saarthak Saxena}
\contact{\href{mailto:saarthaksaxena7@gmail.com}{saarthaksaxena7@gmail.com} \textbar{}
\href{https://www.linkedin.com/in/saarthakiiitd/}{linkedin.com/in/saarthakiiitd} \textbar{}
\href{https://github.com/Saarthakkj}{github.com/Saarthakkj} \textbar{}
\href{https://x.com/curlysaarthak}{x.com/curlysaarthak}}

\sectiontitle{Experience}

\entry{Applied AI Intern}{\textbf{Mar 2026 -- May 2026}}{Brace.so}{}
\vspace{-3pt}
\begin{tightitems}
  \item \textbf{Pedro (Autonomous KG Agent):} Built multi-LLM autonomous agent (Gemini + Claude) maintaining \textbf{10K+} node knowledge graph with zero manual curation. Uses parallel evaluation, deferred decisions for low-confidence cases, semantic similarity for evidence ranking, and parent-child taxonomy classification.
  \item \textbf{Search Engine:} Rebuilt people search ranking with \textbf{LLM-generated structured constraints} (xAI/Grok), replacing fuzzy matching with deterministic exact-match gating for role, company, and location.
  \item \textbf{Oden (Connection Path Discovery):} Practical six-degrees-of-separation engine — finds the \textbf{exact chain of people} between you and any target. Multi-hop pathfinding across \textbf{4,739} actors / \textbf{11,609} edges; \textbf{3.4M+} directed trials, \textbf{99.87\%} success rate. Product output attracted early-stage VC interest.
  \item \textbf{Actor-Relationship Optimization:} Designed scoring via \textbf{60+} experiments reducing processed data to \textbf{2.93\%} of baseline (72 profiles, \textasciitilde{}90K records) while retaining \textbf{98\%} high-quality edges. Cut external API calls \textasciitilde{}60\% via single-pass consolidation.
  \item \textbf{Knowledge Graph Visualizer:} Built full-stack interactive visualizer for exploring and debugging the live 10K+ node graph.
\end{tightitems}
\vspace{-3.5pt}

\entry{ML Engineer}{\textbf{Jun 2025 -- Nov 2025}}{Stealth Startup}{Contract: \textbf{Jul 2025 -- Oct 2025}}
\vspace{-3pt}
\begin{tightitems}
  \item \textbf{Novel GNN from Scratch:} Trained GNN from zero on novel pharmachemistry task + dataset + model under \textbf{\$35} budget. No pretrained weights, no reference implementations, no existing benchmarks.
  \item \textbf{Experimentation at Scale:} Extended GraphGym for \textbf{48k} data points. Orchestrated \textbf{1,000,000+} optimization trials on distributed GPUs and beat Chemprop, the industry standard.
  \item \textbf{Production Delivery:} Shipped lightweight \textbf{2M}-param inference API in \textbf{8 weeks} (full lifecycle: data ingestion to FastAPI + Docker + AWS deployment).
  \item \textbf{Business Impact:} Client used this work to secure a \textbf{INR 30 Lac (\textasciitilde\$35k)} research grant.
\end{tightitems}
\vspace{-3.5pt}

\entry{Software Engineering Intern}{\textbf{Jan 2024 -- May 2024}}{HeydoTech}{}
\vspace{-3pt}
\begin{tightitems}
  \item Developed \textbf{2} automation tools using OpenCV and PyAutoGUI for internal projects.
  \item Collaborated with cross-functional teams of \textbf{5+} to ship feature enhancements improving performance for \textbf{\textasciitilde{}100} users.
  \item Delivered UI/UX improvements with positive feedback from \textbf{80\%} of test users.
\end{tightitems}
\vspace{-2pt}

\sectiontitle{Projects}

\projectentry{\href{https://github.com/Saarthakkj/docbook}{Docbook}}{Python, GraphRAG, CLI \textbar{} \textbf{Apr 2025 -- Present}}
\vspace{-3pt}
\begin{tightitems}
  \item GraphRAG-based CLI tool for intelligent documentation context extraction from single URL input.
  \item Converts URL to full knowledge graph using crawl4ai with automated semantic search and retrieval.
\end{tightitems}

\projectentry{\href{https://github.com/Saarthakkj/course_reccomendation}{Bayesian Course Recommendation System}}{Python, PyTorch, Bayesian ML \textbar{} \textbf{2025}}
\vspace{-3pt}
\begin{tightitems}
  \item Achieved \textbf{0.915} AUC using Bayesian Personalized Ranking (BPR) for implicit feedback recommendations.
  \item Matrix factorization with BPR optimization and probabilistic handling for cold-start problem.
\end{tightitems}
\vspace{-2pt}

\sectiontitle{Education}

\entry{BTech, Electronics and Communication Engineering}{\textbf{Nov 2022 -- Present}}{IIIT Delhi}{}

\end{document}
